---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STRINGutils

<!-- badges: start -->
<!-- badges: end -->

STRINGutils provides additional utilities for [STRINGdb](https://www.bioconductor.org/packages/release/bioc/html/STRINGdb.html) such as getting SVG file of *STRING* network and highlighting features of interest.

## Installation

You can install STRINGutils with:

```{r install}
devtools::install_github("chiasinL/STRINGutils")
```

## Quick demo

For more thorough walkthrough of the package, please see the [vignette](./vignettes/STRINGutils_Vignette.Rmd).

Getting SVG file of STRING network:

```{r, echo = FALSE, result = "hide"}
library(STRINGutils)
data(list = c("example1_mapped", "string_db"))
hits <- example1_mapped$STRING_id[1:200]
```

```{r get_svg}
library(STRINGutils)
get_svg(string_db, hits, file = "my_network.svg")
```
```{r view_svg1, out.width = "80%", fig.cap = "Full network"}
magick::image_read_svg("my_network.svg")
```

If we have a list of proteins of interest, the **full** or **sub-** STRING network of the proteins can be obtained. These proteins will be highlighted by the colors of choice.

For full network:

```{r get_full_network}
plot_features(example1_mapped, colors_vec, string_db, entire = TRUE)
```
```{r view_svg2, out.width = "80%", fig.cap = "Full network"}
magick::image_read_svg("features_of_int.svg")
```

For subnetwork:

```{r get_subnetwork}
plot_features(example1_mapped, colors_vec, string_db)
```
```{r view_svg3, out.width = "80%", fig.cap = "Subnetwork"}
magick::image_read_svg("features_of_int.svg")
```
