---
title: "STRINGutils Vignette"
author: "Chia Sin Liew"
date: "`r format(Sys.time(), '%B %d %Y')`"
output: 
  rmarkdown::html_vignette:
  toc: true
vignette: >
  %\VignetteIndexEntry{STRINGutils Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, results = "hide", warning = FALSE, echo = FALSE}
suppressPackageStartupMessages(c(
  library(STRINGutils),
  library(STRINGdb),
  library(magrittr)
))
```
# Introduction

`STRINGdb R` package provides a convenient way to access the popular STRING
database (https://string-db.org) from `R`. `STRINGutils` is built on top of [`STRINGdb`](https://www.bioconductor.org/packages/release/bioc/html/STRINGdb.html) 
and provides convenient functions to get SVG file of STRING network and 
highlight features of interest.

To prepare data necessary for `STRINGutils`, we first run code from `STRINGdb`
[vignette](https://www.bioconductor.org/packages/release/bioc/vignettes/STRINGdb/inst/doc/STRINGdb.pdf).

Briefly, we map the analyzed data of a microarray study to a human STRING database 
to get STRING identifiers. Please see `STRINGdb` vignette for more information.

```{r from_STRINGdb, message = FALSE}
string_db <- STRINGdb$new(version = "11", species = 9606,
                          score_threshold = 200,
                          input_directory = "")

data("diff_exp_example1")

example1_mapped <- string_db$map(diff_exp_example1, "gene", removeUnmappedRows = TRUE)

hits <- example1_mapped$STRING_id[1:200]
```

## Get SVG of STRING network 

Once we have `string_db`, an instantiated STRINGdb reference class with associated 
information from STRING database, we can run the get SVG function. If `file` is
specified, the SVG will be saved.

```{r get_svg}
xml <- get_svg(string_db, hits)
```
```{r get_svg_file, eval = FALSE}
xml <- get_svg(string_db, hits, file = "my_network.svg")
```

## Get full or subnetwork for proteins of interest

If we have a list of proteins of interest, the **full** or **sub-** STRING network of the proteins can be obtained. These proteins will be highlighted by the colors of choice.

For illustration purposes, here we will pick the top 10 proteins.

```{r pick_top_10}
hits_filt <- example1_mapped %>%
  dplyr::slice_min(pvalue, n = 10, with_ties = FALSE) %>%
  dplyr::filter(!is.na(STRING_id)) # <- filter out proteins with no mapped STRING IDs
```

Let's take a look at the proteins of interest. It is good to know that none of the
top 10 proteins are missing STRING IDs.

```{r top_10_table, echo = FALSE}
knitr::kable(hits_filt, align = "ccc")
```

Next, we need to make a color vector of the same length as our proteins of interest
to specify what colors to highlight our proteins with.

```{r make_color_vec}
colors_vec <- rep("rgb(101,226,11)", nrow(hits_filt))
names(colors_vec) <- hits_filt$gene 
```

Let's take a look at the color vector. 

```{r color_vector} 
colors_vec
```

**Note**: It is important to double check to make sure that the proteins of interest
are matched up to their intended colors. 

Now, we can go ahead and get the network. The function saves the network as a SVG 
file in the current directory as "features_of_int.svg".

For full network:

```{r get_full_network}
plot_features(example1_mapped, colors_vec, string_db, entire = TRUE)
```

The SVG file can be viewed with the `magick::image_read_svg()` function in `RStudio`
viewer.

```{r view_svg1, out.width = "80%", fig.cap = "Full network"}
magick::image_read_svg("features_of_int.svg")
```

The default number of proteins obtained from the network is set to 200. This number can be changed with `n_hits`. The network view mode for STRING network can also be
defined with `network_flavor`. More information about this can be found at STRING's [website](https://string-db.org).

For example, to increase the number of proteins in the network to 500 and use the
network view mode of `confidence` instead of the default `evidence`:

```{r increase_n_hits}
plot_features(example1_mapped, colors_vec, string_db, n_hits = 500, entire = TRUE,
              network_flavor = "confidence")
```
```{r view_svg2, out.width = "80%", fig.cap = "Full network, higher n_hits"}
magick::image_read_svg("features_of_int.svg")
```

For subnetwork:

```{r get_subnetwork}
plot_features(example1_mapped, colors_vec, string_db)
```
```{r view_svg3, out.width = "80%", fig.cap = "Subnetwork"}
magick::image_read_svg("features_of_int.svg")
```


